tag_loss

### 2022-09-21 smelt_2019_winterspring/ZoopPlotting.Rmd
updates to zoop code

# load packages
```{r}
library(tidyverse)
library(lubridate)
library(emmeans)
library(multcomp)
setwd("C:/Users/nkwan/Desktop/Zoop'19")
```

# load data
```{r}
zoop <- read_csv("ZoopDataCombined_biomass_qc'ed_12.19.19.csv")

@@

write_excel_csv(split[["Throw"]], "C:/Users/nkwan/Desktop/Zoop'19/throw_method_zoop.csv")

write_excel_csv(split[["Tow"]], "C:/Users/nkwan/Desktop/Zoop'19/tow_method_zoop.csv")

throw<- read_csv("throw_method_zoop.csv")
tow<- read_csv("tow_method_zoop.csv")
```

@@

write_excel_csv(all, "species.table.csv")
```

@@

tiff(filename="Fig5.tiff", 
    units="in", 
    width=7.25, #or 3.5 for single column
    height=3.75, #height you can adjust according to your plot
    res=600, compression="lzw")
print(z)
dev.off()
```

>>>>

# load packages
```{r}
library(tidyverse)
library(lubridate)
library(emmeans)
library(multcomp)
```

# load data
```{r}
zoop <- read_csv("smelt_2019_winterspring/data_raw/ZoopDataCombined_biomass_qc'ed_12.19.19.csv")

@@

write_excel_csv(split[["Throw"]], "smelt_2019_winterspring/data_raw/throw_method_zoop.csv")

write_excel_csv(split[["Tow"]], "smelt_2019_winterspring/data_raw/tow_method_zoop.csv")

throw<- read_csv("smelt_2019_winterspring/data_raw/throw_method_zoop.csv")
tow<- read_csv("smelt_2019_winterspring/data_raw/tow_method_zoop.csv")
```

@@

write_excel_csv(all, "smelt_2019_winterspring/data_clean/species.table.csv")
```

@@

tiff(filename="smelt_2019_winterspring/figures/zoopfig.tiff", 
    units="in", 
    width=7.25, #or 3.5 for single column
    height=3.75, #height you can adjust according to your plot
    res=600, compression="lzw")
print(z)
dev.off()
```
